---
title: "PML Prediction Assignment Writeup"
author: "Roberto Suárez"
date: "Friday, July 25, 2014"
output: html_document
---




### Exploratory Analysis

We are trying to predict "classe" variable based on all the others contained in training:

```{r,echo=FALSE}
library(caret)

training<-
  read.csv('C:/Users/rsuarez/Documents/github/PracticalMachineLearning/pml-training.csv',
           stringsAsFactors=F)
testing<-
  read.csv('C:/Users/rsuarez/Documents/github/PracticalMachineLearning/pml-testing.csv',
           stringsAsFactors=F)
```
```{r}
str(training)
```


### Preproces 

There are some some variables with so much NA, we are going to put out this variables.

```{r}
Nas<-
  sapply(1:dim(training)[2],
       function(x) sum(is.na(training[,x]))/length(training[,x]))

table(Nas)

training<-
   training[,Nas==0]
# training[sort(sample(1:dim(training)[1],size = 5000,replace = F)),Nas==0]

```

We also have to move out firts seven columns because they are olny user features.

```{r}
training<-
  training[,-c(1:7)]

```


If we pretend make a Random Forest Analysis we have to use only Numeric variables as predictors and a Factor value in the predicted variable.

```{r}
Numeric<-
  sapply(1:dim(training)[2],function(x) class(training[,x])!='character')

Numeric[length(Numeric)]<-T

training<-
  training[,Numeric]

training$classe<-factor(training$classe)
```

### Model fit

We are not using the Random Forest on caret package (train with 'rf' method) just because time of perfomance, function randomForest on randomForest package is so much faster.

```{r}
library(randomForest)

modelFitRF <-
  randomForest(classe~.,training)
```


### Error calculation

As we can this is a very good model fit, its error is only 0.3% approximately and it actually made correct predictions on Submission part of this assigment (20/20).

```{r}
modelFitRF
````


